Generating the Blueprints of Java Ecosystem

### 2015-02-22 msr.tex
almost there with the authors

\author{
  Vassilios Karakoidas\aueb \and Dimitris Mitropoulos\columbia \and Panos Louridas\aueb \and Georgios Gousios\run \and Diomidis Spinellis\aueb\\
  \begin{tabular}{p{7cm} p{5cm} p{5cm}}
   \affaddr{\aueb Department of Management Science and Technology} & \affaddr{\run Department of Digital Security} & \affaddr{\columbia Computer Science Department}\\
   \affaddr{Athens University of Economics and Business} & \affaddr{Radboud University Nijmegen} & \affaddr{Columbia University}\\
   \affaddr{Athens, Greece} & \affaddr{Nijmegen, the Netherlands} & \affaddr{New York, United States}\\
   \email{\{bkarak,louridas,dds\}@aueb.gr} & \email{georgios@cs.ru.nl} & \email{dimitro@cs.columbia.edu}\\
  \end{tabular}
}

>>>>

\author{
  Vassilios Karakoidas\aueb \and Dimitris Mitropoulos\columbia \and Panos Louridas\aueb \and Georgios Gousios\run \and Diomidis Spinellis\aueb\\
  \begin{tabular}{p{6cm} p{5cm} p{5cm}}
   \affaddr{\aueb Dept of Management Science and Technology} & \affaddr{\run Department of Digital Security} & \affaddr{\columbia Computer Science Department}\\
   \affaddr{Athens University of Economics and Business} & \affaddr{Radboud University Nijmegen} & \affaddr{Columbia University}\\
   \affaddr{Athens, Greece} & \affaddr{Nijmegen, the Netherlands} & \affaddr{New York, United States}\\
   \email{\{bkarak,louridas,dds\}@aueb.gr} & \email{georgios@cs.ru.nl} & \email{dimitro@cs.columbia.edu}\\
  \end{tabular}
}
